---
title: "HOW-TO-ROWWISENORM"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HOW-TO-ROWWISENORM}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rowwisenorm)
```


1. Preparation

Reading of the input files
```{r}
data_path1 <- system.file("extdata", "proteingroups.csv", package = "rowwisenorm")
data_path2 <- system.file("extdata", "experimentalDesignProcessed.txt", package = "rowwisenorm")

return_list <- read_files(data_path1, data_path2)
```

Grab the three data frames out of the returned list
```{r}
lowest_level_df <- return_list[["lowest_level_df"]]
exp_design <- return_list[["exp_design"]]
additional_cols <- return_list[["additional_cols"]]
```

Log2 transformation
```{r}
lowest_level_df <- log2_transform(lowest_level_df)
```

Filtering out rows
```{r}
lowest_level_df <- filter_rows(lowest_level_df)
```

Optionally do total sum normalization 
```{r}
lowest_level_df <- sum_normalize(lowest_level_df)
```


2. Normalization

Option 1: References get automatically set
```{r}
lowest_level_df_norm <- normalize_row(lowest_level_df, exp_design)
```

Option 2: Set references as parameter
```{r}
lowest_level_df_norm <- normalize_row(lowest_level_df, exp_design, ref=c("L", "M", "H"))
```

Option 3: Set references interactively
```{r}
# lowest_level_df_norm <- normalize_row(lowest_level_df, exp_design, active = TRUE)
```

Option 4: Use 'sum' as refFunc
```{r}
lowest_level_df_norm <- normalize_row(lowest_level_df, exp_design, refFunc = "sum")
```


3. Output file

Default file name: 'output_rowwisenorm.csv' for lowest level, 
                  'output_rowwisenorm_complete.csv' for complete data
Default location: current working directory

Option 1: Only write the lowest-level data frame with the desired columns into a file
```{r}
write_outfile(lowest_level_df = lowest_level_df_norm)
```

Option 2: Combination of the desired columns with all remaining not-modified columns of the input file
```{r}
write_outfile(lowest_level_df = lowest_level_df_norm, additional_cols = additional_cols)
```

Option 3: Set the name and the directory for the file
```{r}
write_outfile(lowest_level_df = lowest_level_df_norm, additional_cols = additional_cols, filename = "myfile", output_dir = "myout")
```


4. PDF file with plots

Default file name: 'result_rowwisenorm.pdf'
Default location: current working directory

Option 1: Default values for name and location of the file
```{r}
plot_results(lowest_level_df = lowest_level_df_norm, exp_design = exp_design)
```

Option 2: Set the name and the directory for the file
```{r}
plot_results(lowest_level_df = lowest_level_df_norm, exp_design = exp_design, main = "my_rowwisenorm_result", output_dir = "res")
```

Option 3: Set the directory with default name of the file 
```{r}
plot_results(lowest_level_df = lowest_level_df_norm, exp_design = exp_design, output_dir = "res")
```

Option 4: Set the name with the file being saved in current directory
```{r}
plot_results(lowest_level_df = lowest_level_df_norm, exp_design = exp_design, main = "my_rowwisenorm_result")
```

